### 2020-06-11 Report/aws_325ghz_study.tex
updated tables, figures with new channel configurations

\subsubsection{Training}
%  
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz. We assess the performance of the scheme using both three channel and four channel options of 325\,GHz. A separate QRNN is used for each of the 183\,GHz channels. For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz.

@@

The structure of the QRNN is defined by various hyper-parameters which are tuned to achieve a high-performing model. These parameters determine the structure of the neural network and how the network is trained. We performed a grid search to determine structural parameters: depth (number of hidden layers) and width (number of neurons). The quantile loss for the $\tau = 0.5$ (median) is used to compare the performance of different hyper-parameter configurations. Figure~\ref{fig:quantile_loss_median} shows the mean quantile loss when QRNN is trained for predicting clear-sky values for AWS-34. Increasing both layer width and depth has a positive impact on performance of the network, however for four hidden layers, increasing the layer width leads to only small performance gains. On basis of these results, a neural network with four hidden layer and 128 neurons was chosen for training.

For the training, we obtained the best performance when trained with a multiple learning rate schedule. We start the training process with a initial learning rate and after a certain number of epochs, the training is updated with a new initial learning rate. We chose the three training schedules with initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20 epochs. The batch size was set to 256 samples.
%
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{quantile_loss_median.png}
	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
	\label{fig:quantile_loss_median}
\end{figure}
%
\subsection{Prediction accuracy}
%
We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$ and $\pm 2 \sigma$ ($\tau$ = 0.05, 0.32, 0.5 , 0.68, 0.95). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.

To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset. Noise is added to each simulation to mimic a new measurement dataset. The distributions of the predicted clear-sky noise-free values for each of the 183\, GHz channels are shown in Figure~\ref{fig:pdf:qrnn}. The simulated clear-sky distributions are also plotted for reference. It is evident from these results that QRNN is successful in predicting the clear-sky values from measurements.

Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using both three and four channel options of 325\,GHz. Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out. Both the three channel and four channel QRNN model are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric. The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}. For AWS-34, the performance of both three and four option 325\,GHz is comparable. The average bias, standard

The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''. 
   c

@@

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                     & -0.006 & 0.634 &              0.008 &      - \\
uncorrected               & -0.678 & 3.678 &            -10.320 &     - \\
corrected (three channel) &  0.079 & 0.620 &             -0.414 &      2.730 \\
corrected (four channel)  &  0.075 & 0.619 &             -0.416 &      2.957 \\
		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset shown in Figure~\ref{fig:qrnn_C34:deviations}}
	\label{tab:qrnn:C34}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                     &  0.004 & 0.455 &              0.006 &      - \\
uncorrected               & -1.341 & 5.905 &             -7.482 &      - \\
corrected (three channel) & -0.026 & 0.829 &             -2.110 &      4.902 \\
corrected (four channel)  & -0.027 & 0.828 &             -2.187 &      4.906 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
	\label{tab:qrnn:C32}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                     &  0.002 & 0.451 &             -0.017 &     - \\
uncorrected               & -0.981 & 4.706 &             -8.755 &     - \\
 corrected (three channel)&  0.053 & 0.573 &             -0.593 &      4.189 \\
corrected (four channel)  &  0.035 & 0.572 &             -0.554 &      4.280 \\

		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-33.}
	\label{tab:qrnn:C33}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      &  0.002 & 0.626 &             -0.003 &      - \\
uncorrected                & -0.428 & 2.661 &            -12.451 &      - \\
corrected (three channel)  &  0.031 & 0.600 &             -0.303 &      1.451 \\
corrected (four channel)   &  0.049 & 0.581 &             -0.335 &      1.781 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-35.}
	\label{tab:qrnn:C35}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                     & -0.000 & 0.888 &              0.005 &      - \\
uncorrected               & -0.269 & 2.059 &            -11.899 &      - \\
 corrected (three channel)&  0.064 & 0.797 &             -0.138 &      1.263 \\
corrected (four channel)  &  0.057 & 0.765 &             -0.120 &      1.148 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-36.}
	\label{tab:qrnn:C36}
\end{table}

\subsection{Uncertainity estimation}
\section{Discussion}

>>>>

\subsubsection{Training}
%  
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz. A separate QRNN is used for each of the 183\,GHz channels. For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz. We assess the performance of the scheme using both three channel and four channel options of 325\,GHz. Two configurations for three channel option are described in Sec.~\ref{sec:}, and both have been used to train QRNN separately. Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option. Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".

@@

The structure of the QRNN is defined by various hyper-parameters which are tuned to achieve a high-performing model. These parameters determine the structure of the neural network and how the network is trained. We performed a grid search to determine structural parameters: depth (number of hidden layers) and width (number of neurons). The mean quantile loss is used to compare the performance of different hyper-parameter configurations. Figure~\ref{fig:quantile_loss} shows the mean quantile loss when QRNN is trained for predicting clear-sky values for AWS-34 using four channel option. Increasing both layer width and depth has a positive impact on performance of the network, however for four hidden layers, increasing the layer width leads to only small performance gains. On basis of these results, a neural network with four hidden layer and 128 neurons was chosen for training. For the training, we obtained the best performance when trained with a multiple learning rate schedule. We start the training process with a initial learning rate and after a certain number of epochs, the training is updated with a new initial learning rate. We chose the three training schedules with initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20 epochs. The batch size was set to 256 samples.

The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance. 
%
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
	\label{fig:quantile_loss}
\end{figure}
%
\subsection{Prediction accuracy}
%
We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset. Noise is added to each simulation to mimic a new measurement dataset.

The distributions of the predicted clear-sky noise-free values for each of the 183\, GHz channels are shown in Figure~\ref{fig:pdf:qrnn}. The simulated clear-sky distributions are also plotted for reference. For these results, the four channel option was used to train the QRNN. The distributions show that QRNN is overall successful in predicting the clear-sky cases. For all channels, the simulations and predictions have a good agreement for the main peak of the distribution. However, for AWS-32, AWS-33 and  AWS-34, QRNN seems to predict slightly colder TBs. These results give an indication of the behavior of QRNN, but for a detailed analysis of the prediction accuracy, we make a quantitative assessment of the errors.

Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz. Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out. Both the three channel and four channel QRNN model are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric. The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}. . The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''. For AWS-34, the predictions from all three QRNN models are comparable.

@@

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\

		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}}
	\label{tab:qrnn:C34}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       & -0.004 & 0.450 &             -0.030 &      - \\
uncorrected                 & -1.343 & 5.908 &             -7.484 &      - \\
corrected (three-a)  		&  0.019 & 0.889 &             -3.519 &      4.906 \\	 
corrected (three-b)  		& -0.008 & 0.850 &             -3.326 &      4.926 \\			
corrected (four)    		& -0.011 & 0.878 &             -3.030 &      4.930 \\

		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
	\label{tab:qrnn:C32}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       & -0.005 & 0.450 &             -0.004 &      - \\
uncorrected                 & -0.982 & 4.703 &             -8.778 &      - \\
corrected (three-a) 		&  0.088 & 0.583 &             -0.959 &      4.197 \\
corrected (three-b)  		& -0.030 & 0.612 &             -0.756 &      4.205 \\
corrected (four)            &  0.106 & 0.591 &             -1.006 &      4.212 \\
		\hline

	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-33.}
	\label{tab:qrnn:C33}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline

Noise                      &  0.003 & 0.626 &             -0.009 &      - \\
uncorrected                & -0.428 & 2.653 &            -12.492 &      - \\
corrected (three-a) 	   &  0.060 & 0.610 &             -0.281 &      1.439 \\
corrected (three-b) 	   &  0.097 & 0.618 &              0.011 &      1.331 \\
corrected (four)   		   &  0.042 & 0.591 &             -0.351 &      1.821 \\
	\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-35.}
	\label{tab:qrnn:C35}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       & 0.000 & 0.888 &              0.005 &      - \\
uncorrected                 & -0.269 & 2.059 &            -11.899 &      - \\
corrected (three-a) 		&  0.062 & 0.797 &             -0.139 &      1.279 \\
corrected (three-b) 		&  0.092 & 0.770 &             -0.075 &      1.124 \\
corrected (four)   			&  0.056 & 0.779 &             -0.172 &      1.156 \\

		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-36.}
	\label{tab:qrnn:C36}
\end{table}

\subsection{Uncertainty estimation}
%
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{prediction_uncertainty.png}
	\caption{The prediction uncertainty with respect to quantiles for randomly selected 2400 cases.}
	\label{fig:prediction_uncertainty}
\end{figure}

\section{Discussion}
